Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2020-01-20 acks.tex
Add acks for POPL reviewers
First round

\chapter{Acknowledgments}
I thank my supervisor Klaus Ostermann for encouraging me to do a PhD
and for his years of supervision. He has always been patient and kind.

Thanks also to Fritz Henglein for agreeing to review my thesis.

I have many people to thank and too little time to do it properly: I'll finish
these acknowledgments in the final version.

The research presented here has benefited from the help of coauthors,
reviewers and people who offered helpful comments.
Moreover, this PhD thesis wouldn't be possible without all the people who have
supported me, both during all the years of my PhD, but also in the years before.

% From AOSD13

% I thank Sebastian Erdweg for helpful discussions on
% this project, Katharina Haselhorst for help
% implementing the code generator, and the anonymous reviewers, Jacques Carette and Karl Klose
% for their helpful comments on this chapter.

@@

>>>>

\chapter{Acknowledgments}
Writing a PhD thesis is a significant challenge, both professionally and
personally; in a sense, it's a solitary challenge, but in fact I've had so much
help from so many, both in the research and in the personal growth that led me
here. In fact, this page might have been the hardest to write.

I'll start with my professional acknowledgments. I want to thank my supervisor
Klaus Ostermann for encouraging me to do a PhD and for his years of patient and
kind supervision; thanks also to Fritz Henglein for agreeing to review my
thesis. Christian Kästner helped me become a better researcher and writer.
Tillmann Rendel and Sebastian Erdweg sharpened my ability to articulate my
arguments.

Many colleagues helped directly with work presented in this thesis. In
particular, I'd like to thank again my colleagues Cai Yufei, Tillmann, Sebastian
and Philipp Schuster, and my collaborators Lourdes Del Carmen Gonzàlez Huesca and
Yann Règis-Gianas.

% This page was
% Writing a PhD thesis is a significant step in one's life; hence, before thanking
% those who helped my work directly, I want to thank those who helped me become
% the person I am today.

@@

% Pasted again from papers:

% - AOSD13
% I thank Sebastian Erdweg for helpful discussions on
% this project, Katharina Haselhorst for help
% implementing the code generator, and the anonymous reviewers, Jacques Carette and Karl Klose
% for their helpful comments on this chapter.

% - PLDI14:
% We would like to thank Ingo Maier, Erik Ernst,
% Tiark Rompf, Sebastian Erdweg, Christoph Koch and the PLDI '14

% - ESOP19
% \paragraph{Acknowledgments} We are grateful to anonymous reviewers:
% they made important suggestions to help us improve our technical
% presentation.
% We also thank
% Lourdes del Carmen González Huesca,
% Klaus Ostermann, Sebastian Erdweg for helpful discussions on
% this project.
% This work was partially supported by DFG project 282458149
% and by SNF grant No. 200021\_166154.
